---
title: "Reproducible documents"
author: "Hannah Caldwell"
format: html
editor: visual
---

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)
```

## About me

1.  Hannah Grace Caldwell
2.  Department of Nutrition, Exercise and Sports

-   August Krogh Institute
-   University of Copenhagen

I am a **Canadian** working in *Denmark*. I am a cardiovascular exercise physiologist.

## Simple code

```{r}
3 * 3
```

## Testing for Git

At the climbing gym right now.

## Showing the data

```{r}
post_meal_data
glimpse(post_meal_data)
```

## Plot one continuous variable

```{r}
#| fig-cap: "Distribution of BMI."
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

## Exercise: discrete plots

```{r}
#| fig-cap: "Discrete plot of glykemi"
#| label: fig-glykemi-bar
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-glykemi-bar above for a cool plot!

## Plotting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Side by side plots

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side."
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia."
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

#| fig-cap: "BMI and glycemia, side by side."
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia."
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous variables

```{r}
#| fig-cap: "Scatterplot of BMI and the area under the curve for glucose."
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```

## Selecting data

```{r}
select(post_meal_data, Age)
select(post_meal_data, Age, BMI, Weight)
select(post_meal_data, -Group)
```

## Select helpers

```{r}
select(post_meal_data, starts_with("PG"))
select(post_meal_data, ends_with("DXA"))
select(post_meal_data, contains("0"))
```

## Renaming columns

```{r}
small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```

